Ladies' figure skating in the 2002 Winter Olympics

### 2025-12-16 inst/skating.Rmd
extraction methods for ordertable objects

In figure \@ref(fig:rLrO), there is close agreement between the two
methods in the large, but differences in detail.  For example, the
official ordering is hughes first, then slutskaya second, then kwan
third; likelihood winner is slutskya, followed by hughes and then
kwan.  We can gain some understanding of this result by looking at the
raw judging results for the three medallists:

```{r,threemedallists}
skating_table[1:3]
```

@@

```{r justtop7}
(o <- skating_table[1:7])
```

>>>>

In figure \@ref(fig:rLrO), there is close agreement between the two
methods in the large, but differences in detail.  For example, the
official ordering is hughes first, then slutskaya second, then kwan
third; likelihood winner is slutskya, followed by hughes and then
kwan.  We can gain some understanding of this result by looking at the
raw judging results for the three medallists.

# Extraction methods for ordertables

The entire ordertable is given here again for convenience:

```{r,tableagain}
skating_table
```

Suppose we are interested only in `hughes`, `slutskaya`, and `kwan`;
we thus focus on the first three lines of `skating_table`.  If we were
to consider the entries of the first three lines, see how `hughes`
came fourth according to `J2`.  This cannot be converted to a
ranktable because the judges' observations are not sequential.  Each
column should be a permutation of $\left\lbrace 1,2,3\right\rbrace$.
To do this, we use the extraction method:

```{r,threemedallists}
skating_table[1:3,]
```

Above we see just the order for these three competitors.  This may be
converted to a ranktable, or indeed a likelihood function:

```{r,threemedallistsstuff}
as.ranktable(skating_table[1:3,])
suppfun(skating_table[1:3,])
```

@@

```{r justtop7}
(o <- skating_table[1:7,])
```
